\cvsection{Work Experience} % SECTION TITLE
\begin{cventries} % CONTENT
  \cvsimpleentry
  {\textbf{Smarkets, Software Engineer - Backend}} % Job title
  {London, Apr. 2021 - Now} % Date
  {
    \begin{cvitems} % Description
      \item {Joined the exchange team developing a leading betting exchange with \textbf{billions of pounds} in annual traded volume. The team uses \textbf{Rust} and \textbf{C++} for low-latency services, \textbf{Python} for the web servers, \textbf{Postgres} as the database, \textbf{Kafka} as the message queue, and deploys in \textbf{Kubernetes}.}
      \item {Led the project to transition the core exchange's market component from a legacy, monolithic \textbf{Erlang} service to a separate service that uses \textbf{Rust} and \textbf{gRPC}.}
      \item {Migrated the streaming service from \textbf{Python} to \textbf{C++}, using \textbf{C++20 Coroutines}, \textbf{Boost WebSocket}, and \textbf{Boost Signal}. This migration resulted in a \textbf{5x} reduction in resource usage and a \textbf{70\%} decrease in latency.}
      \item {Redesigned the database schema for a critical statement service managing over \textbf{20 TB} of data using Partitioning feature in \textbf{Postgres}. This redesign significantly sped up the cleaning process and elevated query performance.}
      \item {Enhanced system monitoring by proactively integrating metrics and expanding \textbf{Grafana} dashboards.}
      \item {Initiated and developed a new continuous integration pipeline for integration testing, utilizing \textbf{Nix} and \textbf{PyTest}. This pipeline improved the reliability and speed of our development cycle.}
    \end{cvitems}
  }

  \cvsimpleentry
    {\textbf{Sea Group, Software Engineer - Backend}} % Job title
    {Ho Chi Minh, Dec. 2018 - Mar. 2021} % Date
    {
      \begin{cvitems} % Description
        \item {Worked in back-end team of Now, one of the largest food delivery platforms in Vietnam with \textbf{1 million} daily users.}
        \item {Developed customer relationship management (CRM) project for business development team using \textbf{Python}, \textbf{Redis}, and \textbf{Django}.}
        \item {Speeded up report queries by applying \textbf{denormalization model} using \textbf{ElasticSearch}, saving \textbf{90\%} query time and reducing \textbf{5\%} bandwidth usage of the \textbf{MySQL} database.}
        \item {Improved data synchronization workflow by applying message queue using \textbf{Kafka}.}
        \item {Promoted to \textbf{senior software engineer} after 2020.}
      \end{cvitems}
    }

  \cvsimpleentry
    {\textbf{Bioturing, Researcher and developer}} % Job title
    {Ho Chi Minh, Jun. 2017 - Nov. 2018} % Date
    {
      \begin{cvitems} % Description
        \item {Worked in the bioinformatics field using computer science and biological knowledge.}
        \item {Became tech lead of a research team working on command-line tools for processing DNA and RNA data using \textbf{C}.}
        \item {Developed Bioturing Browser, an application for analyzing and visualization of RNA and single-cell sequencing data using \textbf{Javascript, Nodejs}, and \textbf{Electron}.}
      \end{cvitems}
    }

\end{cventries}
